---
title: "an example of exercise with Rmarkdown"
author: "Fanglin"
date: "2026-04-05"
output:
  word_document: default
  pdf_document: default
---

Suggestion to complete exercises in R markdown files, which will allow to combine code chunks, graphical output, and written answers in a single, easy-to-read files.

# hwk-01: understanding the core concepts of R

Assigning 10 and 20 to x and y, respectively.

```{r}
x <- 10
y <- 20
```

Calculating the product of x multiple y, and storing the result in a new object z

```{r}
z <-x * y
z
```

The numbers below are the first ten days of rainfall amounts (0.1, 0.6, 33.8, 1.9, 9.6, 4.3, 33.7, 0.3, 0.0 0.1) in 1996. Create a vector using the c() function.
 
```{r}
rainfall <- c(0.1,0.6, 33.8, 1.9, 9.6, 4.3, 33.7, 0.3, 0.0, 0.1)
```

Based on the vector, and answer the following questions:
1) What was the mean rainfall, how about the standard deviation?

```{r}
mean(rainfall)
sd(rainfall)
```

Which day sawthe highest rainfall (write code to get the answer)?

```{r}
which.max(rainfall)
```

